Not `Won't you be my neighbor?' \\ But `Should you be my neighbor?'

### 2015-04-14 paper_skeleton.tex
rewrote groupprops so that robustness is 0 if network is unconnected and i define corrlength no matterwhat by removing 0 eigenvectors... now can run homogengroupprops for any strategy
about to change paper_skeleton significantly to add an explanation due to the hypergeometric distribution and new greedy opt results

\section{Introduction }
Questions:
\begin{enumerate}
\item How are the two group properties---$\mathscr{H}_2$ robustness and correlation length---related?
\item What are the equilibrium strategies of individuals seeking to optimize their own fitness?
\item What group properties emerge from individual-level optimization?
\end{enumerate}

@@

\begin{equation}
A_{ij}=\left\{\begin{array}{l l l}
1 & \text{ if $i$ pays attention to $j$ }
\\0 & \text{ otherwise }
\end{array}\right.
\end{equation}
If $n_i$ is the number of neighbors node $i$ has, then $n_i=\sum_kA_{ik}$. We assume that having more neighbors means paying less attention to each so we normalize $A$ to find $\bar{A}$: $\bar{A}_{ij}=\frac{A_{ij}}{n_i}$.

The Laplacian of this matrix is given by $L=\bar{A}-I$, which is symmetric only if $A$ is.  We can symmetrize the interactions by defining $S=\frac{1}{2}(A+A^T)$ and $P$ such that $P_{ij}=S_{ij}$ for $j\neq i$ and $P_{ii}=-\sum_kS_{ik}$. Then $L$ and $P$ share the properties that $L\vec{1}=P\vec{1}=\vec{0}$ and that each is negative semi-definite, with the difference being that $P$ is necessarily symmetric.  It is more common to use $L$ in a dynamics system approach, so that 
\begin{equation}
\dot{v}=Lv+D\xi \label{opinion_dynamics}
\end{equation} 
where $D$ is a diagonal matrix with entires $\{\sqrt{n_i}\}$ and $E[\xi(t)]=\vec{0}$, $E[\xi(t)\xi(s)^T]=\frac{1}{2}\delta(t-s)I$, and $E[v(0)\xi(t)^T]=\vec{0}$. This describes a system in which each bird changes averages the differences between its own opinions and those of its neighbors and changes its opinion to minimize these differences. Our choice of $D$ assumes that birds with more neighbors make noisier estimates of how to change their opinions.

@@

So far, we have considered birds whose opinions only depend on the opinions of the rest of the flock. We can additionally incorporate environmental information by assuming that there is an environmental signal such that more informed birds have opinions closer to $1$. If we let $B$ be a matrix with $B_ii=1$ if $i$ can perceive the signal and $0$ otherwise, then the dynamical system becomes
\begin{equation}
\dot{v}=Lv+B(\vec{1}-v)+\xi =L_\text{s}v+B\vec{1}+n_i\xi \label{opinion_dynamics2}
\end{equation}
where $L_\text{s}=L-B$. Similarly, the statistical physics model becomes
\begin{equation}
P(v)=\frac{1}{Z}\exp\left(-\frac{1}{2}(v-\vec{1})^T(-P+B)(v-\vec{1})\right)=\frac{1}{Z}\exp\left(\frac{1}{2}(v-\vec{1})^T(-P_\text{s})(v-\vec{1})\right)
\end{equation}
where $P_\text{s}=P-B$. Again, we can find the covariance matrices $\Sigma_z$, $\Sigma_y$, $C_z$, and $C_y$. As was the case without a signal, if we use $P$ in the dynamical approach and all birds have the same number of neighbors, then we find that $C_y=2\Sigma_y$ (Claim \ref{cov_equivalence}). We define $\rho$ and $\lambda$ as above using the matrices $\Sigma_y$ and $C_z$ in the presence of a signal.

\subsection{Individual-level fitness }
To find the optimal strategies from the individuals' perspectives, we need a measure of individual-level fitness. We use the dynamical system to describe how well each bird learns about the environmental signal. For a given matrix $L$, the expected opinion $q_i$ of each individual satisfies the equations
\begin{equation}
\dot{q}=L_\text{s}q+B\vec{1}. \label{expected_opinion}
\end{equation}
To generate a matrix $L$, we distribute the individuals randomly in space (specifically, in a unit square). has a strategy $n_i$ that dictates how many neighbors it has, so that $n_i=\sum_{j\neq i}{\bf I}(A_{ij}\neq 0)$.    Each individual then pays attention to its $n_i$ nearest neighbors.  One individual is chosen to be a receiver; it and all those individuals within a radius $r$ of the receiver perceive, so that $B_{ii}=1$ for all those birds within this radius. We do this $1000$ times and find $q(1)$ for each matrix, which we refer to as a signaling event. This is meant to simulate a situation in which such that information is present only intermittently and otherwise the birds are moving randomly through space and restructuring their network.

We consider signals that provide information about two types of content: predators and food.  If the signal is information that a predator is present, we assume that whichever individual is least aware of the signal will be predated, i.e. the individual $i$ such that $q_i$ is lowest. Then, fitness is proportional to the probability of surviving, i.e. $1$ minus the probability of being the least informed over many signaling events. If the signal is information that resources are available, we assume that whichever individual is most aware of the signal will get access to the resource, i.e. the individual $i$ such that $q_i$ is highest. In this case, fitness is proportional to the probability of getting the resource, i.e. the probability of being the most informed over many signaling events. The behavior that the birds can change to improve their fitness is the number of other birds they pay attention to, $n_i$. In particular, each individual has a strategy $n_i$ that dictates how many neighbors it has, so that $n_i=\sum_{j\neq i}{\bf I}(A_{ij}\neq 0)$.

@@

\subsection{Robustness and correlation length are positively related. }
In a homogeneous flock, where every bird is using the same strategy, as both the strategy and the radius of the signal change, both $\mathscr{H}_2$ and the correlation length are affected.  Figure \ref{compare_props} shows that there is a relationship between two group properties: the $\mathscr{H}_2$ norm and the correlation length of the flock. 
%%WHY? intuition for why each changes as they do with strategy and radius?!?!?

\subsection{There are multiple ESS, which depend on the content of the signal. }
Surprisingly, even without imposing costs on paying attention to more neighbors, paying attention to the whole flock is not usually the best strategy. The ESS strategy of the number of neighbors to pay attention strongly depends on which selection pressure is being applied.  If a focal bird pays attention to many others, its opinion will be similar to theirs. This will prevent it from being the most informed and hence the first to locate resources. Thus, the uninvadable strategy is to pay attention to few neighbors when selection is due to knowledge about resources. On the other hand, having many neighbors will prevent the focal bird from being the least informed and thus the most likely to be eaten.  Thus, the uninvadable strategy is to pay attention to many neighbors when selection is due to knowledge about predators. Figure \ref{ESS}a shows the ESS strategy when selection is due to knowledge about resources is always lower than the ESS strategy when selection is due to knowledge about predators (Figure \ref{ESS}a).

@@

Figure \ref{ESS_v_H2} shows how the ESS strategy changes as a function of the $\mathscr{H}_2$ robustness.

@@

\subsection{Linear algebra background }

\begin{theorem} \label{lyapeq_theorem}
Given any positive symmetric matrix $Q>0$ there exists a unique positive symmetric matrix $\Sigma>0$ satisfyying $A\Sigma+\Sigma A^T=Q$ if and only if the system $\dot{x}=Ax$ is globally asymptotically stable.
\end{theorem}

@@

\begin{pf}
\begin{align*}
\Sigma_t&=E[y(t)y(t)^T]
\\ \Rightarrow \dot{\Sigma}&=E[\dot{y}(t)y(t)^T+y(t)\dot{y}(t)^T]
\\&=E[(Ay+v+Q\xi)y^T+y(y^TA^T+v^T+\xi^TQ^T)]
\\&=AE[yy^T]+E[yy^T]A^T+vE[y^T]+E[y]v^T+QE[\xi y^T]+E[y\xi^T]Q^T
\\&=A\Sigma_t+\Sigma_tA^T+vE[y^T]+E[y]v^T+QE[\xi y^T]+E[y\xi^T]Q^T.
\end{align*}
Note that we can write a solution to (\ref{tofindsigma}) as 
\begin{equation}
y(t)=\exp(At)y(0)+\int_0^t\exp(A(t-s))vds+\int_0^t\exp(A(t-s))Q\xi(s)ds. \label{sde_solution}
\end{equation}
Eq. (\ref{sde_solution}) allows us to write 
\begin{align*}
E[y(t)]&=\exp(At)y(0)+\int_0^t\exp(A(t-s))vds
\\&=\exp(At)y(0)-A^{-1}\exp(A(t-s))v|_{s=0}^{s=t} \text{ which exists because $A$ has no $0$ eigenvalues }
\\&=\exp(At)y(0)-A^{-1}(I-\exp(At))v.
\end{align*}
Note that if we take the limit as $t$ goes to infinity, 
$$\lim_{t\to\infty}E[(y(t))]=\lim_{t\to\infty}\exp(At)y(0)-A^{-1}(I-\exp(At))v=-A^{-1}v $$ 
since all eigenvalues of $A$ are negative.  Eq. (\ref{sde_solution}) also allows us to write
\begin{align*}
E[y \xi^T]&=\exp(At)y(0)E[\xi(t)^T]+\int_0^t\exp(A(t-s))BE[\xi(t)^T]ds+\int_0^t\exp(A(t-s))QE[\xi(s)\xi(t)]ds
\\&=0+0+\frac{1}{2}Q
\\ \Rightarrow \dot{\Sigma} &= A\Sigma_t+\Sigma_tA^T+vE[y(t)^T]+E[y(t)]v^T+\frac{1}{2}QQ^T+\frac{1}{2}QQ^T
\\ &= A\Sigma_t+\Sigma_tA^T+vE[y(t)^T]+E[y(t)]v^T+QQ^T
\\ \Rightarrow \lim_{t\to\infty} \dot{\Sigma}&=A\Sigma+\Sigma A-vv^T(A^{-1})^T-A^{-1}vv^T+QQ^T
\\ \Rightarrow A\Sigma+\Sigma A&=vv^T(A^{-1})^T+A^{-1}vv^T-QQ^T \text{ since $\dot{\Sigma}=0$ at equilibrium}.
\end{align*}

@@

%%ORGANIZE INTRODUCTION TO THE ROTATION MATRICES. 
We define a matrix $Q\in\R^{N-1}\times\R^N$ such that each row of $Q$ is orthogonal to $\vec{1}$ and the rows are pairwise orthogonal. Young et al. show in \cite{Young:2010fk} show that this equivalent to finding $Q$ such that $Q\vec{1}=\vec{0}$, $QQ^T=I_{N-1}$, and $Q^TQ=I_N-\frac{1}{N}\vec{1}_N\vec{1}_N^T$.  Since the rows of $R$ are orthonormal, $RR^T=I$. Further, since the rows of $R$ are orthonormal, $R$ is invertible, which implies that $R^T=R^{-1}$.  Then we can write

Again, we will use a rotation matrix $R\in\R^N\times\R^N$ such that the last row of $R$ is $\frac{1}{\sqrt{N}}\vec{1}$ and the other rows are normal and orthogonal to $\vec{1}$.
Above, we found a $Q\in\R^{N-1}\times\R^N$ such that each row of $Q$ was orthogonal to $\vec{1}$ and $R\in\R^N\times\R^N$ be the matrix with $\frac{1}{\sqrt{N}}\vec{1}^T$ as its last row and the first $N-1$ rows identical to the rows of $Q$. Then $R$ is a rotation matrix, so $RR^T=R^TR=I$ and $\det(R)=1$. This allows us to
\[
 \boxed{\bar{y}=Rx$, $y=Qx=\bar{y}_{i=1}^{N-1}$ (or $y=RQ^TQx$), $z=Q^TQx$, $V=\frac{1}{N}\sum_ix_i}
 \]

 Depending on the model framework, we will find either $E[yy^T]$ or $E[zz^T]$. This are interchangeable since $E[yy^t]=E[Rzz^TR^T]=RE[zz^T]R^T$ and $E[zz^T]=E[R^Tyy^TR]=R^TE[yy^T]R$.

>>>>

\section{Introduction }
%Introduction to schools and flocks
%
%Reasons for flocking / paying attention to your peers. Predation \cite{Ballerini:2007uq} Empirical evidence for reduced predator efficiency when the prey are a in a bigger group (captive fish) \cite{Landeau:1986fk}. Foraging (find citations). Foraging (cite bat / information center papers). I have to make some statement to the effect that I assume predator efficiency is constant irrespective of the type of network the flock forms or if it's even connected.  Which is conservative.
%
%How to construct a social network: Zone model a la Couzin uses metric interaction rules. Metric zones seem to reproduce flocking dynamics in surf scoters \cite{Lukeman:2010vn}.  Evidence for topological network in starlings \cite{Ballerini:2007uq}, which they suggest must rely on vision \cite{Ballerini:2007uq}, although this can produced by a model in which an interaction range is governed by absolute distance instead of number of neighbors \cite{Bode:2010ys}. Evidence that the ability to see one's neighbors should be included in constructing social networks (golden shiners) \cite{Strandburg-Peshkin:2013fk}
%
%evidence for six to seven neighbors from anisotropy of positions of neighbors \cite{Ballerini:2007uq}  Ballerini argues that six / seven represents a cognitive limitation \cite{Ballerini:2007uq}. maximum likelihood interaction range is around ten \cite{Bialek:2012fk}
%
%assertion that individuals are trying to maintain a cohesive group "The main goal of the interaction among individuals is to maintain cohesion of the group. This cohesion is a very strong biological requirement, shaped by the evolutionary pressure for survival: Stragglers and small groups are significantly more prone to predation than animals belonging to large and highly cohesive aggregations." \cite{Ballerini:2007uq}, the support for which comes from a paper about teleost fishes. But why should the group maintain cohesion due to a predator response if predation is the thing causing cohesion? There's something circular here. And "An alternative interpretation of the interaction range we find is that the specific value of $n_\text{c}$ may be functional to optimize anti predatory response: If each individual interacts with too few neighbors, information is non noisy, but it is too short-ranged; conversely, if the interaction involves too many neighbors, information is averaged over several ill-informed individuals, and it is too noisy" \cite{Ballerini:2007uq} --- BUT WE FIND THE OPPOSITE. "The interaction mechanism shaped by evolution must keep cohesion in the face of strong perturbations, of which predation is the most relevant. We believe that topological interaction is the only mechanisms granting such robust cohesion and, therefore, higher biological fitness." \cite{Ballerini:2007uq} 
%
%Evidence for how collective create interesting structures \cite{Cavagna:2009kx} \cite{Bialek:2013fk} \cite{Young:2013kx}
%
%Individual evolution, consequences for group structure\cite{Torney:2015fk}
%
%NOTE: A similar model of random flock dynamics is in \cite{Shang:2014uq}. They randomly place nodes in a unit square repeatedly, but they let them keep their opinions across spatial shuffles. They prove that the system exponentially approaches consensus in the absence of noise and show that the system almost always reaches consensus in the presence of noise \cite{Shang:2014uq}. With or without noise, the time to consensus decreases as the number of neighbors increases, but with diminishing returns, as in \cite{Young:2013kx}.
%
%Can individual optimization reproduce interesting group structure?
%
%CRITICALITY AS AN INFORMATIONAL TRAGEDY OF THE COMMONS.
%
%Two points to make about optimization in a group: 1) \cite{Torney:2015fk} found that when one individual changes its strategy it does not change the overall social environment and thus can optimize without regard for the group. However, to find the group-level optimum, one must change the group's strategy and thus the social environment, leading to an group optimum different from the individual's. Same here. 2) The existence of multiple ESS is evidence for how important social environment is because what is an un-invadable strategy when it is at high frequency does poorly when another strategy is at high frequency.
%
Questions:
\begin{enumerate}
\item How are the two group properties---$\mathscr{H}_2$ robustness and correlation length---related?
\item What are the equilibrium strategies of individuals seeking to optimize their own fitness?
\item What group properties emerge from individual-level optimization?
\end{enumerate}

@@

\begin{equation}
A_{ij}=\left\{\begin{array}{l l l}
1 & \text{ if $i$ pays attention to $j$ }
\\0 & \text{ otherwise }
\end{array}\right.
\end{equation}
If $k_i$ is the number of neighbors node $i$ has, then $k_i=\sum_kA_{ik}$. We assume that having more neighbors means paying less attention to each so we normalize $A$ to find $\bar{A}$: $\bar{A}_{ij}=\frac{A_{ij}}{k_i}$.

The Laplacian of this matrix is given by $L=\bar{A}-I$, which is symmetric only if $A$ is.  We can symmetrize the interactions by defining $S=\frac{1}{2}(A+A^T)$ and $P$ such that $P_{ij}=S_{ij}$ for $j\neq i$ and $P_{ii}=-\sum_kS_{ik}$. Then $L$ and $P$ share the properties that $L\vec{1}=P\vec{1}=\vec{0}$ and that each is negative semi-definite, with the difference being that $P$ is necessarily symmetric.  It is more common to use $L$ in a dynamics system approach, so that 
\begin{equation}
\dot{v}_i=\frac{1}{k_i}\sum_i\left(v_j-v_i\right)+\sqrt{k_i}\xi_i
\end{equation}
\begin{equation}
\dot{v}=Lv+D\xi \label{opinion_dynamics}
\end{equation} 
where $D$ is a diagonal matrix with entires $\{\sqrt{k_i}\}$ and $E[\xi(t)]=\vec{0}$, $E[\xi(t)\xi(s)^T]=\frac{1}{2}\delta(t-s)I$, and $E[v(0)\xi(t)^T]=\vec{0}$. This describes a system in which each bird changes averages the differences between its own opinions and those of its neighbors and changes its opinion to minimize these differences. Our choice of $D$ assumes that birds with more neighbors make noisier estimates of how to change their opinions.

@@

So far, we have considered birds whose opinions only depend on the opinions of the rest of the flock. We can additionally incorporate environmental information by assuming that there is an environmental signal such that more informed birds have opinions closer to $1$. If we let $B$ be a matrix with $B_ii=1$ if $i$ can perceive the signal and $0$ otherwise, then the dynamical system becomes
\begin{equation}
\dot{v}=Lv+B(\vec{1}-v)+D\xi =L_\text{s}v+B\vec{1}+D\xi \label{opinion_dynamics2}
\end{equation}
where $L_\text{s}=L-B$. Similarly, the statistical physics model becomes
\begin{equation}
P(v)=\frac{1}{Z}\exp\left(-\frac{1}{2}(v-\vec{1})^T(-P+B)(v-\vec{1})\right)=\frac{1}{Z}\exp\left(\frac{1}{2}(v-\vec{1})^T(-P_\text{s})(v-\vec{1})\right)
\end{equation}
where $P_\text{s}=P-B$. Again, we can find the covariance matrices $\Sigma_z$, $\Sigma_y$, $C_z$, and $C_y$. As was the case without a signal, if we use $P$ in the dynamical approach and all birds have the same number of neighbors, then we find that $C_y=2\Sigma_y$ (Claim \ref{cov_equivalence}). We define $\rho$ and $\lambda$ as above using the matrices $\Sigma_y$ and $C_z$ in the presence of a signal.

\subsection{Individual-level fitness }
To find the optimal strategies from the individuals' perspectives, we need a measure of individual-level fitness. We use the dynamical system to describe how well each bird learns about the environmental signal. For a given matrix $L$, the expected opinion $q_i$ of each individual satisfies the equations
\begin{equation}
\dot{q}=L_\text{s}q+B\vec{1}. \label{expected_opinion}
\end{equation}
To generate a matrix $L$, we distribute the individuals randomly in space (specifically, in a unit square). has a strategy $k_i$ that dictates how many neighbors it has, so that $k_i=\sum_{j\neq i}{\bf I}(A_{ij}\neq 0)$.    Each individual then pays attention to its $k_i$ nearest neighbors.  One individual is chosen to be a receiver; it and all those individuals within a radius $r$ of the receiver perceive, so that $B_{ii}=1$ for all those birds within this radius. We do this $1000$ times and find $q(1)$ for each matrix, which we refer to as a signaling event. This is meant to simulate a situation in which such that information is present only intermittently and otherwise the birds are moving randomly through space and restructuring their network.  If, instead of paying attention to the closest neighbors, a bird choose $k_i$ neighbors at random out of $N$ birds, $N_\text{I}$ of whom are informed, the number of informed neighbors follows a hypergeometric distribution:
\begin{equation}
P(j \text{ informed neighbors} )=\frac{{N_\text{I}\choose j}{N-N_\text{I}\choose k_i-j}  }{{N\choose k_i}}. \label{hypergeom}
\end{equation} 
This distribution is not an exact description of the probability of $j$ informed neighbors in our model  since it ignores spatial proximity, but it is a useful approximation for considering the advantages and disadvantages of each strategy $k_i$.

We consider signals that provide information about two types of content: predators and food.  If the signal is information that a predator is present, we assume that whichever individual is least aware of the signal will be predated, i.e. the individual $i$ such that $q_i$ is lowest. Then, fitness is proportional to the probability of surviving, i.e. $1$ minus the probability of being the least informed over many signaling events. If the signal is information that resources are available, we consider two levels of resource abundance. If there are scarce resources, we assume that whichever individual is most aware of the signal will get access to the resource, i.e. the individual $i$ such that $q_i$ is highest. In this case, fitness is proportional to the probability of getting the resource, i.e. the probability of being the most informed over many signaling events. If there are abundant resources, we assume that the first four individuals to the resources can share it, so that fitness is proportional to the probability of being one of the four most informed birds. Finally, we consider a combination of predation and resources: fitness is proportional to the $1$ minus the probability of being predated times the probability of being the most informed. The behavior that the birds can change to improve their fitness is the number of other birds they pay attention to, $k_i$. In particular, each individual has a strategy $k_i$ that dictates how many neighbors it has, so that $k_i=\sum_{j\neq i}{\bf I}(A_{ij}\neq 0)$.

@@

\subsection{Robustness and correlation length are positively related. }
In a homogeneous flock, where every bird is using the same strategy, as both the strategy and the radius of the signal change, both $\mathscr{H}_2$ and the correlation length are affected.  Figure \ref{compare_props} shows that both $\mathscr{H}_2$ and correlation length are maximized at intermediate strategies when the radius is low and at low strategies when the radius is high. We prove in the Appendix (Appendix Claim \ref{cov_equivalence}) that if we use a symmetric matrix to calculate $\rho$ and all birds have the same number of neighbors $n$, then the covariance matrices used to calculate $\rho$ and $\lambda$ are identical up to a constant, which suggests that the two properties cannot be optimized independently.

\subsection{There are multiple ESS, which depend on the content of the signal. }
Surprisingly, even without imposing costs on paying attention to more neighbors, paying attention to the whole flock is not always the best strategy. The ESS strategy of the number of neighbors to pay attention strongly depends on which selection pressure is being applied.

Those birds that can perceive the environmental signal will always have better information than those that cannot. Selection, therefore, acts to improve a bird's ability to learn about the signal when it cannot perceive it.  In Appendix Claim \ref{exp_approx} we show that an uninformed bird's opinion can be approximated by $\sum_{\text{informed }j}L_{ij}$, that is the total weight given to informed birds.  Being the most well-informed uninformed bird, therefore, amounts to having the highest proportion of informed neighbors and being the least well-informed amounts to having the smallest proportion of informed neighbors. As described above, the hypergeometric distribution is a good approximation for the probability distribution of the number of informed neighbors a bird with strategy $k_i$ will have. As shown in Figure \ref{hypergeo}, under the hypergeometric distribution, having many neighbors makes it unlikely that few of those neighbors will be uninformed, but it also makes it unlikely that all of them will be uninformed (Figure \ref{hypergeo}).

These observations explain the ESS number of neighbors we find.

If a focal bird pays attention to many others, its opinion will be similar to theirs. This will prevent it from being the most informed and hence the first to locate resources. Thus, the uninvadable strategy is to pay attention to few neighbors when selection is due to knowledge about resources. On the other hand, having many neighbors will prevent the focal bird from being the least informed and thus the most likely to be eaten.  Thus, the uninvadable strategy is to pay attention to many neighbors when selection is due to knowledge about predators. Figure \ref{ESS}a shows the ESS strategy when selection is due to knowledge about resources is always lower than the ESS strategy when selection is due to knowledge about predators (Figure \ref{ESS}a).
%%a different explanation: Having many neighbors means that your opinion will be close to the average opinion of the group. Even if some of your many neighbors or informed, others will not be, and your opinion will be somewhere in between. If you have few neighbors, on the other hand, your opinion will often be at the extremes of the group: low, if you have few informed neighbors, and high, if you have many informed neighbors. To avoid being in the bottom of the group, therefore, you should avoid having few neighbors. To try to be in the top, on the other hand, having few neighbors is a good strategy. I think maybe this a more intuitive way to say it?

@@

%Figure \ref{ESS_v_H2} shows how the ESS strategy changes as a function of the $\mathscr{H}_2$ robustness.

@@

\subsection{Linear algebra claims and theorems }

\begin{claim} 
\label{exp_approx}
Suppose. $v(t)$ satisfies $\dot{v}=Av+f$ with $v(0)=v_0$, where $A$ has no $0$ eigenvalues. If $V$ is the matrix of eigenvectors of $A$ and $\Lambda$ is diagonal with the eigenvalues of $A$, then
\begin{equation} \label{diffeq_solution}
v(t)=V\exp(t\Lambda)V^{-1}v_0+V\Lambda^{-1}(\exp(t\Lambda)-I)V^{-1}f.
\end{equation}
We can approximate $v(t)\approx V\exp(t\Lambda)V^{-1}v_0+V(tI+\frac{t^2}{2}A)V^{-1}f$ if the eigenvalues are not too far from $0$. In the case that $A=L_\text{f}$ and $f=B\vec{1}$, this suggests that for $i$ that cannot perceive the signal, $v_i(t)\approx \frac{t^2}{2}\sum_{\text{informed }j }L_{ij}.$ This approximation is reasonable for $i$ such that $B_{ii}=0$, but worse for $i$ such that $B_{ii}\neq 0$. 
\end{claim}

\begin{pf}
First we show that (\ref{diffeq_solution}) solves the differential equation. Note that if $A=V\Lambda V^{-1}$.
\begin{align*}
\dot{v}&=V\Lambda \exp(t\Lambda)V^{-1}v_0+V\Lambda^{-1}(\Lambda\exp(t\Lambda))V^{-1}f
\\&=V\Lambda V^{-1}V\exp(t\Lambda)V^{-1}v_0+V\exp(t\Lambda)V^{-1}f
\\&=AV\exp(t\Lambda)V^{-1}v_0+V\exp(t\Lambda)V^{-1}f-VV^{-1}f+VV^{-1}f
\\&=AV\exp(t\Lambda)V^{-1}v_0+V(\exp(t\Lambda)-I)V^{-1}f+f
\\&=AV\exp(t\Lambda)V^{-1}v_0+V\Lambda V^{-1}V \Lambda^{-1}(\exp(t\Lambda)-I)V^{-1}f+f
\\&=AV\exp(t\Lambda)V^{-1}v_0+A\Lambda^{-1}(\exp(t\Lambda)-I)V^{-1}f+f
\\&=Av(t)+f.
\end{align*}
If $g(x)=\frac{1}{x}(\exp(ax)-1)$, then $g(x)\approx a+\frac{a^2}{2}x$ for $x$ close to $0$. Then, if the eigenvalues of $A$ are not too far from $0$, $\Lambda^{-1}(\exp(t\Lambda)-I)\approx  tI+\frac{t^2}{2}\Lambda$.  If $A=L_\text{f}$, then all eigenvalues of $A$ are negative.  If $N_\text{I}$ is the number of informed individuals, i.e. $i$ such that $B_{ii}\neq0$, then there are $N_\text{I}$ eigenvalues of $A$ close to $-2$ such that, if  $k$ is the index of one of these eigenvalues, $V_{ik}$ is large if and only if $i$ is informed.  The rest of the $N-N_\text{I}$ eigenvalues are between $-2$ and $0$ and, if $k$ is the index of one of these eigenvalues, $V_{ik}$ is large if and only if $i$ is uninformed. Therefore, the eigenvalue approximation is worst for the informed individuals and best for the uninformed individuals. Using the eigenvalue approximation, $v(t)$ becomes 
\begin{align*}
v(t)=V\exp(t\Lambda)V^{-1}v_0+tVV^{-1}B\vec{1}+\frac{t^2}{2}V\Lambda V^{-1}B\vec{1}=V\exp(t\Lambda)V^{-1}v_0+tB\vec{1}+\frac{t^2}{2}L_\text{f}B\vec{1}
\end{align*}
Ignoring the informed individuals and the initial conditions, this gives $v_i(t)\approx \sum_{\text{informed } j}L_{ij}$.
\end{pf}

\begin{theorem} \label{lyapeq_theorem}
Given any positive symmetric matrix $Q>0$ there exists a unique positive symmetric ] matrix $\Sigma>0$ satisfyying $A\Sigma+\Sigma A^T=Q$ if and only if the system $\dot{x}=Ax$ is globally asymptotically stable.
\end{theorem}
\begin{pf}
Proof available elsewhere.
\end{pf}

@@

\begin{pf}
\begin{align*}
\Sigma_t&=E[y(t)y(t)^T]
\\ \Rightarrow \dot{\Sigma}&=E[\dot{y}(t)y(t)^T+y(t)\dot{y}(t)^T]
\\&=E[(Ay+v+Q\xi)y^T+y(y^TA^T+v^T+\xi^TQ^T)]
\\&=AE[yy^T]+E[yy^T]A^T+vE[y^T]+E[y]v^T+QE[\xi y^T]+E[y\xi^T]Q^T
\\&=A\Sigma_t+\Sigma_tA^T+vE[y^T]+E[y]v^T+QE[\xi y^T]+E[y\xi^T]Q^T.
\end{align*}
Note that we can write a solution to (\ref{tofindsigma}) as 
\begin{equation}
y(t)=\exp(At)y(0)+\int_0^t\exp(A(t-s))vds+\int_0^t\exp(A(t-s))Q\xi(s)ds. \label{sde_solution}
\end{equation}
Eq. (\ref{sde_solution}) allows us to write 
\begin{align*}
E[y(t)]&=\exp(At)y(0)+\int_0^t\exp(A(t-s))vds
\\&=\exp(At)y(0)-A^{-1}\exp(A(t-s))v|_{s=0}^{s=t} \text{ which exists because $A$ has no $0$ eigenvalues }
\\&=\exp(At)y(0)-A^{-1}(I-\exp(At))v.
\end{align*}
Note that if we take the limit as $t$ goes to infinity, 
$$\lim_{t\to\infty}E[(y(t))]=\lim_{t\to\infty}\exp(At)y(0)-A^{-1}(I-\exp(At))v=-A^{-1}v $$ 
since all eigenvalues of $A$ are negative.  Eq. (\ref{sde_solution}) also allows us to write
\begin{align*}
E[y \xi^T]&=\exp(At)y(0)E[\xi(t)^T]+\int_0^t\exp(A(t-s))BE[\xi(t)^T]ds+\int_0^t\exp(A(t-s))QE[\xi(s)\xi(t)]ds
\\&=0+0+\frac{1}{2}Q
\\ \Rightarrow \dot{\Sigma} &= A\Sigma_t+\Sigma_tA^T+vE[y(t)^T]+E[y(t)]v^T+\frac{1}{2}QQ^T+\frac{1}{2}QQ^T
\\ &= A\Sigma_t+\Sigma_tA^T+vE[y(t)^T]+E[y(t)]v^T+QQ^T
\\ \Rightarrow \lim_{t\to\infty} \dot{\Sigma}&=A\Sigma+\Sigma A^T-vv^T(A^{-1})^T-A^{-1}vv^T+QQ^T
\\ \Rightarrow A\Sigma+\Sigma A^T&=vv^T(A^{-1})^T+A^{-1}vv^T-QQ^T \text{ since $\dot{\Sigma}=0$ at equilibrium}.
\end{align*}

@@

\begin{fact}
If $V=\sum_iv_i/N$ and $C=\left(E[(v_i-V)(v_j-V)]\right)_{ij}$, then $\sum_{ij}C_{ij}=0$.
\end{fact}
\begin{pf}
\begin{align*}
\sum_{ij}E[(v_i-V)(v_j-V)]&=\sum_{ij}\left(E[v_iv_j]-E[v_iV]-E[v_jV]+E[VV]\right)
\\&=\sum_{ij}E[v_iv_j]-N\sum_iE[v_iV]-N\sum_jE[v_jV]+N^2E[VV]
\\&=\sum_{ij}E[v_iv_j]-\sum_{ij}E[v_iv_j]-\sum_{ij}E[v_iv_j]+\sum_{ij}E[v_iv_j]
\\&=0
\end{align*}
\end{pf}

In the following sections of the Appendix, transforming an opinion vector $x$ will be useful.  To do so, we define a matrix $Q\in\R^{N-1}\times\R^N$ such that each row of $Q$ is orthogonal to $\vec{1}$ and the rows are pairwise orthogonal. Young et al. show in \cite{Young:2010fk} show that this equivalent to finding $Q$ such that $Q\vec{1}=\vec{0}$, $QQ^T=I_{N-1}$, and $Q^TQ=I_N-\frac{1}{N}\vec{1}_N\vec{1}_N^T$.  We next define a rotation matrix $R\in\R^N\times\R^N$ such that the last row of $R$ is $\frac{1}{\sqrt{N}}\vec{1}^T$ and the other rows are given by the rows of $Q$. Since the rows of $R$ are orthonormal, $RR^T=I$ and $R$ is invertible, which implies that $R^T=R^{-1}$. If $z=Q^TQx$, then $z_i=v_i-\frac{1}{N}\sum_iv_i$. Similarly, if $\bar{y}=Rx$, then $\bar{y}_N=\frac{1}{\sqrt{N}}\sum_ix_i$ and $y=(\bar{y}_1,\dots,\bar{y}_{N-1})^T=Qx$ gives the component of $v$ that is orthogonal to the consensus vector $\vec{1}$. We can also translate between $y$ and $z$ by noting that $z=Q^Ty$ and $y=QQ^Tz$ or $y$ is given by the first $N-1$ coordinates of $Rz$.

\begin{equation} \label{transformations}
 \boxed{V=\frac{1}{N}\sum_ix_i ,\ z=Q^TQx=x-V\vec{1}, \ \bar{y}=Rx,\ y=Qx=\bar{y}_{i=1}^{N-1}}
 \end{equation}
